Reanalysis Step 4: Propensity Score Analysis with Twang

### 2025-09-12 reanalysis-4-propensity_scores.qmd
balance stat

    # Extract the weighted (after matching) standardized effect sizes
    # The bal.table contains effect sizes for each covariate
    if (!is.null(bal_table$es.mean) && !is.null(bal_table$es.mean$max.es)) {
      largest_smds[i] <- bal_table$es.mean$max.es
    } else {
      # Fallback: use the summary method
      model_summary <- summary(twang_model)
      if (!is.null(model_summary) && "max.es" %in% names(model_summary)) {
        largest_smds[i] <- model_summary$max.es
      } else {
        largest_smds[i] <- NA
      }
    }
  }, error = function(e) {
    # If balance table fails, set to NA
    largest_smds[i] <- NA
  })
}

>>>>

    # Extract the weighted (after matching) standardized effect sizes
    # For ATT with es.mean stop method, the balance table is stored in bal_table$es.mean.ATT
    if (!is.null(bal_table$es.mean.ATT) && !is.null(bal_table$es.mean.ATT$std.eff.sz)) {
      # Get the maximum absolute standardized effect size
      largest_smds[i] <- max(abs(bal_table$es.mean.ATT$std.eff.sz), na.rm = TRUE)
    } else if (!is.null(bal_table$es.mean) && !is.null(bal_table$es.mean$std.eff.sz)) {
      # Fallback to es.mean if es.mean.ATT not available
      largest_smds[i] <- max(abs(bal_table$es.mean$std.eff.sz), na.rm = TRUE)
    } else {
      # Try to get from the twang_model summary directly
      largest_smds[i] <- twang_model$desc$es.mean$max.es
    }
  }, error = function(e) {
    # If balance table fails, try to get from model summary
    tryCatch({
      largest_smds[i] <- twang_model$desc$es.mean$max.es
    }, error = function(e2) {
      largest_smds[i] <- NA
    })
  })
}
